Quantum Hoare Type Theory

### 2020-06-12 ms-paper/ms-paper.tex
WIP
Better notation for semantic proof obligation

@@

Finally, the judgement $\Delta; \Psi; \Gamma_1 \Longrightarrow \Gamma_2$ encodes the sequent calculus for the assertion logic. Recall that $\Delta$, $\Psi$, and $\Gamma$ denote the variable context, the quantum heap context and the assertion context, respectively.

@@

\begin{mathpar}
	\inferrule
	{\Delta \vdash M \chk \type{Qbit}
		\\ \Delta; \Psi; P \Longrightarrow (M \hookrightarrow -)
		\\ \Delta, x:\type{Bool}; P \circ ((M \mapsto -) \multimap \kw{emp}) \vdash E \syn y:B . Q}
	{\Delta; P \vdash x \Leftarrow \kw{measQbit} M; E \syn y:B. (\exists x:\type{Bool}.Q)}
\end{mathpar}

@@

>>>>

\newcommand{\prove}{\models}

@@

Finally, the judgement $\Delta; \Psi; \Gamma_1 \prove \Gamma_2$ encodes the sequent calculus for the assertion logic. Recall that $\Delta$, $\Psi$, and $\Gamma$ denote the variable context, the quantum heap context and the assertion context, respectively.

@@

\begin{mathpar}
	\inferrule
	{\Delta \vdash M \chk \type{Qbit}
		\\ \Delta; \Psi; P \prove (M \hookrightarrow -)
		\\ \Delta, x:\type{Bool}; P \circ ((M \mapsto -) \multimap \kw{emp}) \vdash E \syn y:B . Q}
	{\Delta; P \vdash x \Leftarrow \kw{measQbit} M; E \syn y:B. (\exists x:\type{Bool}.Q)}
\end{mathpar}

@@

\begin{mathpar}
	\inferrule
	{ \exists \Psi . (emp * \top) \vdash q \Leftarrow mkQbit false; return measQbit q \chk r : Bool . \forall \Psi . (emp \multimap emp \wedge Id(r, false)) }
	{do (q \Leftarrow mkQbit false; return measQbit q) \chk \{emp\} r : Bool \{emp \wedge Id(r, false)\}}
\end{mathpar}
